---
title: "Chinese Personnel and Organization Work Timeline (组织人事工作大事记)"
format: 
  html:
    interactive: true
---

## What this is: 

Below, you will find an interactive visualization / explorer for personnel and organization work in the Chinese Reform Era (1978-1997). In total, there are about 2700 organization work entries and 170 personnel work entries. Naturally, there's some overlap between these entries, but they are not the same, and even when they note the same event, the events are glossed differently. 

I compiled these entries from three sources I collected, scanned, OCR'd, and manually corrected: first, three timelines of significant events from the Research Office of the Central Organization Department: one covering 1978-1988, another covering 1989-1992, and a third covering 1993-1997. These were dedicated publications that cover not just relevant meetings, speeches, the release of relevant reports, and some statistics, but also the appointments and removals of significant figures. To these, I also added a less-exhaustive set of "personnel work" events from Xu and Sun's 2009 book, "Reform of China's Personnel Institutions, 1978-2008" (for the overlapping years).^[中共中央组织部研究室《党的组织工作大事记》(1978-1988,1989-1992,1993-1997); 徐颂陶 & 孙建立,《中国人事制度改革（1978-2008）》.]

As you explore, please do note that the format of the entries changes over time; while some entries were possible to separate, other entries list *multiple discrete events* that took place on the same day.^[I'd suggest making good use of the search function on the Shiny app to ensure you don't miss things, and of course the Chinese version here is the authoritative version.]

I hope that this resource will be useful anyone interested in the changes in Chinese history, the study of institutional reform, organization work, or personnel appointments in China for this period. 

## Explore the data! 

Below you should be able to explore the (translated) data in an interactive way. If it's not working or displaying correctly, or if you'd like to view the original Chinese, please check out the [shiny app version](https://mthompsonbrusstar.shinyapps.io/zuzhirenshi/).


```{r, echo=FALSE}
#| warning: false
#| message: false

library(tidyverse)
library(readr)
library(crosstalk)
library(plotly)
library(reactable)
library(htmltools)

data <- read_csv("组织人事工作大事记1978-1997.csv") %>%
  select(type,start_date,translated_text) %>%
  mutate(category = case_when(type == "人事工作" ~ "Personnel Work",
                              type == "组织工作" ~ "Org. Work")) %>%
  select(-type) %>%
  rename(
    event_en = translated_text,
    date_start = start_date
  )

shared_data <- SharedData$new(data)
```

### Filters

```{r, echo = F}
#| warning: false
#| message: false
filter_slider("date", "Date Range", shared_data, ~date_start)
filter_checkbox("type", "Event Category", shared_data, ~category)
```

### Histogram of Entries over Time

```{r, echo = F}
#| warning: false
#| message: false
plot_ly(shared_data, x = ~date_start, type = "histogram", color = ~category) %>%
  layout(bargap = 0.1,
         xaxis = list(title = "Year"),
         yaxis = list(title = "Event Count"))
```

### Entry Table

```{r, echo = F}
#| warning: false
#| message: false

reactable(
  shared_data,
  columns = list(
    date_start = colDef(name = "Start Date"),
    category = colDef(name = "Category"),
    event_en = colDef(name = "Event")
  )
)
```
